Social Closeness and Dishonesty \thanks{Replication files are available on the author's Github account \url{https://github.com/saidejp/social_closeness}}

### 2019-03-04 Manuscript/social_closeness_dishonesty.Rmd
From tiff to jpeg
.

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ~/Documents/R/github_Said/social_closeness/social_closeness_dishonesty_files/svm-latex-ms.tex
title: "Social Closeness and Dishonesty"
thanks: "Replication files are available on the author's Github account..."
author:
- name: Said E. Jiménez
  affiliation: Universidad Nacional Autónoma de México
- name: Roberto Mercadillo
  affiliation: Universidad Autónoma Metropolitana
- name: Eduardo Garza-Villarreal
  affiliation: Instituto Nacional de Psiquiatría Ramón de la Fuente Muñiz
abstract: "This document provides an introduction to R Markdown, argues for its..."
keywords: "pandoc, r markdown, knitr"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
# spacing: double
bibliography: ~/Dropbox/master.bib
biblio-style: apsr
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ~/Documents/R/github_Said/social_closeness/Manuscript/social_closeness_dishonesty_files/svm-latex-ms.tex
title: "Social Closeness and Dishonesty"
thanks: "Replication files are available on the author's Github account https://github.com/saidejp/social_closeness"
author:
- name: Said E. Jiménez
  affiliation: Universidad Nacional Autónoma de México
- name: Roberto Mercadillo
  affiliation: Universidad Autónoma Metropolitana
- name: Eduardo Garza-Villarreal
  affiliation: Instituto Nacional de Psiquiatría Ramón de la Fuente Muñiz
abstract: "This document provides an introduction to R Markdown, argues for its..."
keywords: "dishonesty, bayesian hierarchical modeling, mixture modeling"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
fig_caption: yes
# spacing: double
bibliography: ~/Dropbox/master.bib
biblio-style: apsr
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# Introduction

bla bla...

# Method

![Rates](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g1.jpeg)

![Rates by partner](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g2.jpeg)

![Rates by partners and promise condition](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g3.jpeg)

![Promises](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g4.jpeg)

![Bayesians logistic coefficients](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g5.jpeg)

![Linear population predictor](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g6.jpeg)

![Linear population predictor by subject](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g7.jpeg)

![Population coefficient with uncertainty](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g8.jpeg)

![Model adjusted by subject](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g9.jpeg)

![Two latent thetas](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g16.jpeg)

![Subjects from two latent thetas](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g10.jpeg)

![Strategies by group](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g11.jpeg)

![Rates by group](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12.jpeg)

![Rates by group and promise condition](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12_b.jpeg)

![Reaction times by group](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g13.jpeg)

![Reaction times by partner](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g14.jpeg)

![Difference between groups in reaction time](/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g15.jpeg)

### 2019-03-04 Manuscript/social_closeness_dishonesty.tex
From tiff to jpeg
.

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}

@@

\title{Social Closeness and Dishonesty \thanks{Replication files are available on the author's Github account\ldots{}}  }

@@

\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Said E. Jiménez (Universidad Nacional Autónoma de México) and Roberto Mercadillo (Universidad Autónoma Metropolitana) and Eduardo Garza-Villarreal (Instituto Nacional de Psiquiatría Ramón de la Fuente Muñiz)},
             pdfkeywords = {pandoc, r markdown, knitr},  
            pdftitle={Social Closeness and Dishonesty},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

\vskip 8.5pt \noindent \emph{Keywords}: pandoc, r markdown, knitr \par

@@

\noindent  \subsection{R Markdown}\label{r-markdown}

This is an R Markdown document. Markdown is a simple formatting syntax
for authoring HTML, PDF, and MS Word documents. For more details on
using R Markdown see \url{http://rmarkdown.rstudio.com}.

When you click the \textbf{Knit} button a document will be generated
that includes both content as well as the output of any embedded R code
chunks within the document. You can embed an R code chunk like this:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(cars)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##      speed           dist       
##  Min.   : 4.0   Min.   :  2.00  
##  1st Qu.:12.0   1st Qu.: 26.00  
##  Median :15.0   Median : 36.00  
##  Mean   :15.4   Mean   : 42.98  
##  3rd Qu.:19.0   3rd Qu.: 56.00  
##  Max.   :25.0   Max.   :120.00
\end{verbatim}

\subsection{Including Plots}\label{including-plots}

You can also embed plots, for example:

\includegraphics{social_closeness_dishonesty_files/figure-latex/pressure-1.pdf}

Note that the \texttt{echo\ =\ FALSE} parameter was added to the code
chunk to prevent printing of the R code that generated the plot.
\newpage
\singlespacing 
\bibliography{\textasciitilde{}/Dropbox/master.bib}
\end{document}

>>>>

@@

\title{Social Closeness and Dishonesty \thanks{Replication files are available on the author's Github account
\url{https://github.com/saidejp/social_closeness}}  }

@@

\@ifpackageloaded{color}{
    \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
    \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Said E. Jiménez (Universidad Nacional Autónoma de México) and Roberto Mercadillo (Universidad Autónoma Metropolitana) and Eduardo Garza-Villarreal (Instituto Nacional de Psiquiatría Ramón de la Fuente Muñiz)},
             pdfkeywords = {dishonesty, bayesian hierarchical modeling, mixture modeling},  
            pdftitle={Social Closeness and Dishonesty},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

\vskip 8.5pt \noindent \emph{Keywords}: dishonesty, bayesian hierarchical modeling, mixture modeling \par

@@

\noindent  \section{Introduction}\label{introduction}

bla bla\ldots{}

\section{Method}\label{method}

\begin{figure}
\centering
\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g1.jpeg}
\caption{Rates}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g2.jpeg}
\caption{Rates by partner}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g3.jpeg}
\caption{Rates by partners and promise condition}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g4.jpeg}
\caption{Promises}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g5.jpeg}
\caption{Bayesians logistic coefficients}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g6.jpeg}
\caption{Linear population predictor}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g7.jpeg}
\caption{Linear population predictor by subject}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g8.jpeg}
\caption{Population coefficient with uncertainty}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g9.jpeg}
\caption{Model adjusted by subject}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g16.jpeg}
\caption{Two latent thetas}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g10.jpeg}
\caption{Subjects from two latent thetas}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g11.jpeg}
\caption{Strategies by group}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12.jpeg}
\caption{Rates by group}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g12_b.jpeg}
\caption{Rates by group and promise condition}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g13.jpeg}
\caption{Reaction times by group}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g14.jpeg}
\caption{Reaction times by partner}
\end{figure}

\begin{figure}
\centering
\includegraphics{/Users/saidjimenez/Documents/R/github_Said/social_closeness/Manuscript/figures/g15.jpeg}
\caption{Difference between groups in reaction time}
\end{figure}
\newpage
\singlespacing 
\bibliography{\textasciitilde{}/Dropbox/master.bib}
\end{document}
